\jaxcosmo: End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-03-04 paper.tex
polish

Although the above mentioned MCMC packages are widely used and are very valuable, they do not take benefit of recent advance in automatic differentiation (aka \textit{autodiff}) \citep{2015arXiv150205767G, 2018arXiv181105031M} which is widely used in neural network optimization and more generally for machine learning and computational statistics as for instance Hamiltonian Monte Carlo sampling and Variational Inference, two subjects covered in this paper. The \textit{autodiff} has been implemented in widely used libraries as for instance \texttt{Stan}\footnote{\url{https://mc-stan.org/users/documentation}} \citep{JSSv076i01} and \texttt{TensorFlow}\footnote{\url{https://www.tensorflow.org/}}  \citep{tensorflow2015-whitepaper} or \texttt{PyTorch}\footnote{\url{https://pytorch.org/docs/}} \citep{NEURIPS2019_9015}.

>>>>

Even if the above mentioned MCMC packages are widely used and are very valuable, they do not take benefit of recent advance in automatic differentiation (aka \textit{autodiff}) \citep{2015arXiv150205767G, 2018arXiv181105031M} which is widely used in neural network optimization and more generally for machine learning and computational statistics as for instance Hamiltonian Monte Carlo sampling and Variational Inference, two subjects covered in this paper. The \textit{autodiff} has been implemented in widely used libraries as for instance \texttt{Stan}\footnote{\url{https://mc-stan.org/users/documentation}} \citep{JSSv076i01} and \texttt{TensorFlow}\footnote{\url{https://www.tensorflow.org/}}  \citep{tensorflow2015-whitepaper} or \texttt{PyTorch}\footnote{\url{https://pytorch.org/docs/}} \citep{NEURIPS2019_9015}.
